Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
multiple changes outlining basics of approach section

@@

@@

OVERVIEW OF THE REST OF THE PAPER

@@

>>>>

\usepackage{graphicx}

\newcommand{\arclabel}[1]{\ensuremath{\stackrel{#1}{\to}}}
\newcommand{\precision}[1]{\ensuremath{\textrm{Prec}\left(#1\right)}}
\newcommand{\recall}[1]{\ensuremath{\textrm{Recall}\left(#1\right)}}

@@

TO DO: DISCUSS TUNING'S VIRTUES, FLAWS

@@

TO DO: OVERVIEW OF THE REST OF THE PAPER

@@

This work explores a family of dependency pair match (DPM) measures
that are composed of precision and recall combinations over various
decompositions of a syntactic dependency tree. These measures are
extensions of the dependency-pair F measures found in
\cite{roark06:sparseval,owczarzak07labelleddepseval}.  Rather than
comparing string sequences, as BLEU does with its $n$-gram precision,
this approach defers to a parser for an indication of the relevant
words that indicate more about its meaning --- in these
implementations, the head on which that word depends.  Each sentence
(both reference and hypothesis) is converted to a labeled syntactic
dependency tree and then relations from each tree are extracted and
compared.

A member of this family is defined by several parameters.  The first
of these parameters is the nature of the decomposition of the
dependency tree structure.  A \emph{decomposition list} is the list of
ways in which the tree is reduced to a bag of tree-local
tuples. Figure~\ref{fig:decompexample}
\begin{figure}
  \centering
  \begin{tabular}{rcc}
    & \textbf{Reference} & \textbf{Hypothesis} \\
    \textbf{dependency tree}
    & \includegraphics[scale=0.6]{dpm-example-ref.eps} & 
    \includegraphics[scale=0.6]{dpm-example-hyp.eps}\\
    \textbf{$dlh$ list} &
    \begin{tabular}{@{$\langle$}c@{,~}c@{,~}c@{$\rangle$}}
      the & \arclabel{\texttt{det}}  &  cat \\
      red & \arclabel{\texttt{mod}}  &  cat \\
      cat & \arclabel{\texttt{subj}} &  ate \\
      ate & \arclabel{\texttt{root}} &  $<$root$>$ \\
    \end{tabular} & 
    \begin{tabular}{@{$\langle$}c@{,~}c@{,~}c@{$\rangle$}}
      the &      \arclabel{\texttt{det}}  &  cat \\
      cat &      \arclabel{\texttt{subj}} &  stumbled \\
      stumbled & \arclabel{\texttt{root}} &  $<$root$>$ \\
    \end{tabular}\\
  \end{tabular}\\
  Precision$_{dlh}$ is $\frac{1}{3}$ and Recall$_{dlh}$ is
  $\frac{1}{4}$, so $F[dlh] = \frac{2}{7}$
  \caption{Example hypothesis and reference dependency trees and the $dlh$ decomposition of each.}
  \label{fig:decompexample}
\end{figure}
illustrates the \emph{dependency-link-head} decomposition of the
dependency tree into a list of $\langle d, l, h \rangle$ tuples.  Some
members of the DPM family may apply more than one decomposition; other
good examples are the $dl$ decomposition, which generates a bag of
dependent word with outbound links, and the $lh$ decomposition, which
generates a bag of inbound link labels, with the head word for each
included.

It is worth noting here that the $dlh$ and $lh$ decompositions (but
not the $dl$ decomposition) ``overweight'' the headwords, in that
there are $n$ elements in the resulting bag, but if a word has no
dependents it is found in the resulting bag exactly one time (in the
$dlh$ case) or not at all (in the $lh$ case).  Conversely,
syntactically ``key'' words, that are directly modified by many other
words in the tree, are included multiple times in the decomposition
(once for each inbound link).  We argue that this overcounting is a
virtue; the syntactic structure indicates which words are more
important to translate correctly.

We may not completely trust the parser's best parse.  The parser
itself, if we use a probabilistic parser, can provide an $n$-best
parse list forest for the translation reference and translation
hypothesis. We use the probability statistics of the forest to compute
expected counts for each decomposition. Though this approach yields
partial counts, standard comparisons like precision and recall are
still valid.

When multiple decomposition types used together, we may combine these
subscores in a variety of ways.  We may compute precision and recall
subscores for each decomposition separately, or, since the results of
each decomposition are of different types entirely, we may compute
them as members of one large bag for an even simpler F score.  These
two approaches are equivalent when only one decomposition type is
included.  For simplicity in presentation, we use the following
notation, where $dl$ and $lh$ represent the two kinds of
decompositions described above and $\mu_h$ represents a harmonic mean:
\begin{eqnarray}
  \label{eq:fprmeans}
  F[dl,lh] & = &
  \mu_h \left( \precision{dl \cup lh},
    \recall{dl \cup lh} \right) \\
  \mu_{PR}[dl,lh]  & = & \mu_h \left( \precision{dl},
    \recall{dl}, \precision{lh}, \recall{lh} \right)    
\end{eqnarray}
Dependency-based SParseval and Owczarzak \textit{et al.}'s
\cite*{owczarzak07labelleddepseval} \textbf{d} approach, then, may
each be understood as $F[dlh]$, while the latter's \textbf{d\_var}
method may be understood as something close to $F[dl,lh]$.
